Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Addition of McCall et al definitions (as found in Van  Vliet)

\begin{defn}
  A measure of the ease of installation.  \wss{Where does this definition come
    from? Please add a citation.  I believe it is from \citet{McCallEtAl1977},
    but you should verify this.}
\end{defn}

@@

\begin{defn}
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

Verifiability involves ``solving the equations right'' \citep[p.~23]{Roache1998};
it benefits from rational documentation that systematically shows, with explicit
traceability, how the governing equations are transformed into code.
\oo{Verifiability is sometimes referred to as testability, so I culled some
  testability definitions here}

@@

@@

@@

@@

@@

\subsection{Portability \pmi{owner}}
\begin{defn}
The ease with which a system or component can be transferred from one hardware
or software environment to another \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
An application is portable across a class of environments to the degree that the
effort required to transport and adapt it to a new environment in the class is
less than the effort of redevelopment \citep{mooney1990strategies}.
\end{defn}
\begin{defn} \label{PortabilityDefnSelected}
Effort required to transfer the program from one hardware and/or software system
environment to another \citep{pressman2005software}.
\end{defn}
\begin{defn}
A set of attributes that bear on the ability of software to be transferred from
one environment to another (including the organizational, hardware, of software
environment)\citep{pfleeger2006software}.
\end{defn}
\begin{defn}
Code possesses the characteristic of portability to the extent that it can be
operated easily and well on computer configurations other than its current
one. This implies that special function features, not easily available at other
facilities, are not used, that standard library functions and subroutines are
selected for universal applicability, and so on \citep{boehm2007software}.
\end{defn}
\begin{defn}
Portability refers to the ability to run a system on different hardware
platforms \citep{ghezzi1991fundamentals}.
\end{defn}

@@

>>>>

\begin{defn}
  A measure of the ease of installation.  \wss{Where does this definition come
    from? Please add a citation.  Is it from \citet{McCallEtAl1977}?  I thought
    so originally, but after looking into it, I don't think so anymore.}
\end{defn}

@@

\begin{defn}
  ``The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

Verifiability involves ``solving the equations right'' \citep[p.~23]{Roache1998};
it benefits from rational documentation that systematically shows, with explicit
traceability, how the governing equations are transformed into code.
\oo{Verifiability is sometimes referred to as testability, so I culled some
  testability definitions here}  \wss{culled means removed - is that your
  intention?}

\wss{In case we need it, here is a definition of testability.}

\begin{defn}
  ``The effort required to test a program to ensure that it performs its
  intended function'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  ``The extent to which a program can be expected to perform its intended
  function with required precision'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  ``The effort required to learn, operate, prepare input, and interpret output
  of a program'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  ``The effort required to locate and fix an error in an operational program''
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.) \wss{It looks
    like \citet{pressman2005software} was using \citet{McCallEtAl1977} for their
    definition.}
\end{defn}

@@

\begin{defn}
  ``The extent to which a program (or parts thereof) can be reused in other
  applications'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\subsection{Portability \pmi{owner}}
\begin{defn}
The ease with which a system or component can be transferred from one hardware
or software environment to another \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
An application is portable across a class of environments to the degree that the
effort required to transport and adapt it to a new environment in the class is
less than the effort of redevelopment \citep{mooney1990strategies}.
\end{defn}
\begin{defn} \label{PortabilityDefnSelected}
Effort required to transfer the program from one hardware and/or software system
environment to another \citep{pressman2005software}.
\end{defn}
\begin{defn}
A set of attributes that bear on the ability of software to be transferred from
one environment to another (including the organizational, hardware, of software
environment)\citep{pfleeger2006software}.
\end{defn}
\begin{defn}
Code possesses the characteristic of portability to the extent that it can be
operated easily and well on computer configurations other than its current
one. This implies that special function features, not easily available at other
facilities, are not used, that standard library functions and subroutines are
selected for universal applicability, and so on \citep{boehm2007software}.
\end{defn}
\begin{defn}
Portability refers to the ability to run a system on different hardware
platforms \citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
  ``The effort required to transfer a program from one hardware and/or software
  environment to another'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  ``The effort required to copule one system with another''
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn}
